Autonomous Realization of Simple Machines

### 2014-05-26 doc/paper/paper.tex
1/4 left in results

DONT READ HERE YET!

A significant challenge in accomplishing the series of the autonomous manipulation and perception
tasks has been the accumulation of error over the course of the executions. To remedy such an error
build-up, at the current state of our work, the authors intervene and instruct the robot to minimize
its position errors. We focus on the two main reasons and propose possible solutions.

During experiments, we observed that the RGBD data becomes more erroneous as the distance increases.
Within a 1 meter bound, the mean error is within 2-3 cm whereas with the maximum 4 meters (e.g. the
room limits), we see errors up to 10 cm. The proportional increase of error with respect to distance
suggest a camera calibration problem. Another source of error could be the slack in the tilt and pan
joints that control the camera view. The general of camera calibration has been addressed via bundle
adjustment in \cite{dasgupta1999making}.

A second reason we suspect that might lead to localization errors is the error accumulated while the
robot attempts to follow a velocity profile in the forward direction. Figure \ref{fig:controller} demonstrates the
reference position and velocity trajectories (green), along with the real trajectories (red). To
remedy this error, we will focus on the trajectory following techniques developed by \cite{ha1996trajectory}.

\begin{figure}[ht!] 
  \centering
  \includegraphics[width=0.6\linewidth]{Figures/controller.png}
  \caption{The mechanical advantage in forces}
  \label{fig:controller}
\end{figure}

>>>>

A challenge in long-term manipulation tasks is the accumulation of error over the course of the
executions. To remedy such an error build-up, at the current state of our work, the authors
intervene and instruct the robot to minimize its error if necessary. One of the main causes of this
inaccuracy is the reliability of the RGBD data. We observe that a mean error of 2-3 cm within a 1 m
bound increases up to 10 cm with 4 meters. The proportional increase in error with respect to
distance suggest a camera calibration problem which can be addressed with bundle adjustment \cite{dasgupta1999making}.

Secondly, locomotion for heavy balancing robots is an active research area and our implementation
with a proportional-derivative controller can be improved following techniques as presented in
\cite{ha1996trajectory}. A major challenge is the system modeling, specifically accurate center of
mass and inertia information. Figure \ref{fig:controller} demonstrates the behavior of the robot as
it follows a velocity profile, moving straight. The sinusoidal behavior in the output position
trajectory (red) is the robot regaining its balance and the steady state error may be accommodated
with an integral term in the controller. A concern is the high-frequency velocity sinusoids which may cause instability when heavy objects are manipulated.

\begin{figure}[ht!] 
  \centering
  \includegraphics[width=0.9\linewidth]{Figures/controller.png}
  \caption{The mechanical advantage in forces}
  \label{fig:controller}
\end{figure}

\subsection{}
